Testing Charts: viewer's perceptual accuracy in surveys

### 2023-07-19 SDSS-2023/testing-charts-accuracy.qmd
re-ran the paper as pdf. The colors help a lot :)

>>>>

\hh{Not sure where should put this, parking it here for right now:}
\hh{expectations - start}
What we call 'aligned' and 'unaligned', here, is similar to Cleveland and McGill's set of rankings, but with some modifications:
both 'aligned' and 'unaligned' bars (in tests 1 and 2) or wedges (in test 3) share the same axis. Aligned tiles are additionally anchored in the same position in one dimension, i.e. the difference between their sizes can be reduced to a positional assessment. Unaligned tiles do not share this anchor, however, the context of the other tiles in the chart provide a frame, which *should* help with an assessment of the tiles' sizes beyond a comparison of (arc) lengths or areas.   
We would expect that comparing unaligned tiles is a harder task (with correspondingly lower levels of accuracy) than a comparison of aligned tiles, with the framing given by the context of the other tiles in the same column (or the same pie) mitigating some of this difficulty. @fig-tasks-explain gives an overview of the comparisons of tasks 1 through 3 and the closest corresponding tasks in Cleveland and McGill.

```{r}
#| label: fig-tasks-explain
#| fig-cap: Comparisons made in charts in the Cleveland and McGill ranking

cat("still working on the chart")
```

\hh{expectations - end}
